\documentclass[11pt,a4paper]{article}

% ------------------ PACKAGES ------------------
\usepackage[left=1.5cm,right=1.5cm,top=1.3cm,bottom=1.3cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{mathptmx}

% ------------------ COLORS ------------------
\definecolor{heading}{HTML}{000000}

% ------------------ HYPERREF ------------------
\hypersetup{
    hidelinks
}

% ------------------ SECTION FORMAT ------------------
\titleformat{\section}
  {\bfseries\large\color{heading}}
  {}
  {0em}
  {}
  [\vspace{3pt}\titlerule]

\titlespacing{\section}{0pt}{8pt}{4pt}

% ------------------ LIST SETTINGS ------------------
% All bullets slightly indented for alignment under headings
\setlist[itemize]{
    leftmargin=1.8cm,
    labelsep=0.5em,
    itemsep=1pt,
    topsep=1pt
}

\pagenumbering{gobble}

\begin{document}

% ================= HEADER =================
\begin{center}
    {\LARGE \textsc{Hadeed Ul Hassan}} \\[4pt]
    Islamabad, Pakistan
\end{center}

\vspace{-8pt}

% ================= CONTACT =================
\begin{center}
\small
\faEnvelope\ \href{mailto:hadeed.hassan189@gmail.com}{hadeed.hassan189@gmail.com}
\quad $\vert$ \quad
\faPhone\ +92 326 9908189
\quad $\vert$ \quad
\faGlobe\ \href{https://pro-hadi.netlify.app}{Portfolio}
\quad $\vert$ \quad
\faLinkedin\ \href{https://www.linkedin.com/in/hadeed-ulhassan-b91453376}{LinkedIn}
\quad $\vert$ \quad
\faGithub\ \href{https://github.com/hadiid1718}{GitHub}
\end{center}

\vspace{-12pt}

% ================= EDUCATION =================
\section*{Education}

\textbf{Quaid-i-Azam University} \hfill \textit{Sep. 2022 -- June 2026} \\ 
\hangindent=0.6cm \textit{Bachelor of Science in Information Technology (BSIT)} \hfill \textit{Islamabad, Pakistan}

\vspace{0pt}

\textbf{Relevant Coursework:} \\
\hangindent=0.6cm Web Programming, Database Management Systems, Advanced Web Engineering, Software Engineering, Data Structures \& Algorithms

% ================= PROFESSIONAL SUMMARY =================
\section*{Professional Summary}
\hangindent=0.6cm 
Results-driven Full Stack MERN Developer with 1.5+ years of professional experience building scalable web applications and automation tools. Specialized in developing high-performance React UIs, secure RESTful APIs, and full-stack solutions. Proven track record delivering 15+ client projects with 99.8\% uptime, maintaining 5-star Fiverr rating with 95\% client retention. Strong expertise in debugging complex codebases, optimizing application performance, and converting requirements into production-ready solutions.

% ================= CORE RESPONSIBILITIES =================
\section*{Core Responsibilities}
\begin{itemize}
    \item Developed full-stack web applications using React.js, Node.js, Express.js,  and modern JavaScript (ES6+).
    \item Built responsive and reusable UI components with Tailwind CSS, Material-UI, and Bootstrap ensuring cross-browser and mobile compatibility.
    \item Designed and implemented RESTful APIs with JWT authentication handling 100K+ monthly API calls with sub-200ms response times.
    \item Managed application state and client-side data flow using Redux Toolkit, Context API, and React Hooks.
    \item Implemented authentication, authorization, and protected routes using JWT, OAuth 2.0, and session-based methods.
    \item Designed, queried, and maintained databases using MongoDB, and MySQL with optimized indexing strategies.
    \item Handled server-side validation, error handling, middleware integration, and business logic implementation.
    \item Optimized frontend rendering and backend performance through code splitting, lazy loading, and efficient database queries.
    \item Debugged, tested, and maintained existing codebases resolving 200+ production issues ensuring stability and scalability.
    \item Integrated third-party APIs including Stripe payment gateway, Google Maps API, AWS S3, and Socket.io for real-time features.
    \item Managed project workflows using Git, GitHub, Trello, and Jira participating in agile ceremonies for timely delivery.
\end{itemize}

% ================= EXPERIENCE =================
\section*{Experience}

\textbf{Fiverr} \hfill \textit{July 2024 -- Present} \\
\hangindent=0.6cm\textit{Freelance Full Stack Developer} \hfill \textit{Remote, Pakistan}
\begin{itemize}
    \item Generated qualified projects through Fiverr and direct client outreach by actively researching potential clients and maintaining consistent communication.
    \item Built secure RESTful APIs with JWT authentication and role-based access control for enterprise-level applications.
    \item Implemented responsive designs achieving 98+ Google Lighthouse scores across performance, accessibility, and SEO metrics.
    \item Reduced client project delivery time by 40\% through reusable component libraries and automated deployment pipelines.
\end{itemize}

% ================= RELEVANT WORK =================
\section*{Key Projects}

\textbf{Universal File Converter \& Compressor}
\begin{itemize}
    \item Engineered multi-format file conversion application supporting 20+ file types with batch processing.

    \item \textbf{Tech:} React.js, Node.js, Express.js, MongoDB, socket.io,redis, docker, chart.js, Tailwind CSS
\end{itemize}

\textbf{Upwork Automation Tool}
\begin{itemize}
    \item Developed automation platform increasing productivity by 3x through automated job searching and bidding.
    \item Implemented Redis caching reducing database queries by 65\% and created dashboard tracking 50+ metrics.
    \item \textbf{Tech:} React.js, Node.js, Puppeteer, MongoDB, Redis
\end{itemize}

\textbf{Departmental Voting System}
\begin{itemize}
    \item Built secure voting platform supporting 1,000+ concurrent users with JWT authentication.
    \item Utilized Socket.io for real-time updates achieving sub-second latency handling 50K+ votes.
    \item \textbf{Tech:} React.js, Node.js, Express.js, MongoDB, Socket.io, JWT
\end{itemize}

\textbf{Zentry Gaming Platform}
\begin{itemize}
    \item Developed gaming platform with React.js,Gsap,framer-motion.
    \item Built interactive UI with animations achieving 60fps and optimized bundle size by 45\%.
    \item \textbf{Tech:} React.js,Gsap, Framer-motion, Tailwind CSS, Node.js, 
\end{itemize}

\textbf{Airbnb Clone}
\begin{itemize}
    \item Created rental marketplace with advanced search, Stripe payment integration, and Google Maps API.
    \item Built booking system with calendar availability and dual-interface for owners and renters.
    \item \textbf{Tech:} React.js, Node.js, Express.js, MongoDB, Stripe, Google Maps API
\end{itemize}



% ================= ACADEMIC PROJECTS =================
\section*{Academic Projects}

\textbf{Admission Portal System (PHP)}
\begin{itemize}
    \item Developed admission management system with student registration and admin panel for merit list generation.
    \item \textbf{Tech:} PHP, MySQL, Bootstrap, jQuery
\end{itemize}

\textbf{Admission Portal System (MERN)}
\begin{itemize}
    \item Re-engineered portal using MERN stack with JWT authentication and role-based access control.
    \item \textbf{Tech:} React.js, Node.js, Express.js, MongoDB
\end{itemize}

\textbf{E-commerce Platform}
\begin{itemize}
    \item Built shopping platform with product catalog, Stripe payment integration, and admin dashboard.
    \item \textbf{Tech:} React.js, Node.js, Express.js, MongoDB, Stripe
\end{itemize}

\textbf{Real-Time Chat Application}
\begin{itemize}
    \item Created messaging application with Socket.io supporting group chat and message history.
    \item \textbf{Tech:} React.js, Node.js, Socket.io, MongoDB
\end{itemize}

% ================= TECHNICAL SKILLS =================
\section*{Technical Skills}

\hangindent=0.6cm \textbf{Frontend:} React.js, Next.js, JavaScript (ES6+), TypeScript, HTML5, CSS3 \\
\textbf{UI Libraries:} Tailwind CSS, Material-UI, Bootstrap, Shadcn UI, Framer Motion \\
\textbf{Backend:} Node.js, Express.js, PHP, RESTful APIs, GraphQL, Microservices Architecture \\
\textbf{Databases:} MongoDB, , MySQL, Redis, \\
\textbf{Authentication:} JWT, OAuth 2.0, Session Management, Role-Based Access Control \\
\textbf{DevOps \& Tools:} Git, GitHub, Docker, AWS (EC2, S3), Heroku, Vercel, Netlify, CI/CD Pipelines \\
\textbf{Testing:} React Testing Library, Postman \\
\textbf{Other:} Socket.io, WebSockets, Stripe Integration, Google Maps API,

% ================= LANGUAGES =================
\section*{Languages}

\hangindent=0.6cm \textbf{English:} Professional Working Proficiency \quad \textbf{Urdu:} Native/Bilingual Proficiency

\end{document}